Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?

### 2018-09-13 outputs/docs/events/svm-rmarkdown-article-example.Rmd
Update the paper format and minor improvements to the column splitter

---
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
author:
  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: true
bibliography: ../bibliography.bib
abstract: |
  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the mid-1800s through to 2017. We find that 1) changes of government where the party in power also changes, result in significant changes in topics discussed in parliament, but when the party does not change the topics are unchanged; 2) polling results do not have a significant effect; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change.

---

@@

# Introduction
New governments often go out of their way to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was supported by all living former Prime Ministers apart from his immediate predecessor. Similarly,  Similarly, significant events can alter the course of a government. For instance, consider the change in the Howard government after the 9/11 attacks. However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party? And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?

@@

```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'}
document_1 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.40, 0.40, 0.1, 0.05, 0.05)
  )

document_2 <- tibble(
  Topics = c(
  "topic 1", "topic 2", "topic 3", "topic 4", "topic 5"
  ),
  Probability = c(0.01, 0.04, 0.35, 0.20, 0.4)
  )

par(mfrow=c(2,1))
ggplot(document_1, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 1") +
  coord_cartesian(ylim = c(0, 0.4))

ggplot(document_2, aes(Topics, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over topics for Document 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

@@

```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'}
topic_1 <- tibble(
  Terms = c(
  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
  ),
  Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2)
  )

topic_2 <- tibble(
  Terms = c(
  "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english"
  ),
  Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142)
  )

# par(mar = c(4, 4, 0.1, 0.1))
ggplot(topic_1, aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over terms for Topic 1") +
  coord_cartesian(ylim = c(0, 0.4))
ggplot(topic_2, aes(Terms, Probability)) +
  geom_point() +
  theme_classic() +
  labs(title = "Distribution over terms for Topic 2") +
  coord_cartesian(ylim = c(0, 0.4))
```

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: svm-latex-ms.tex
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
thanks: "Thank you to X, Y and Z for their helpful comments, guidance and suggestions. **Version as of**: `r format(Sys.time(), '%B %d, %Y')`; **Comments welcomed**: rohan.alexander@anu.edu.au"
author:
- name: Monica Alexander
  affiliation: University of Toronto
- name: Rohan Alexander
  affiliation: Australian National University
abstract: "We use a structural text model to explore the effect of various events on what was said in Australian state and federal parliaments from the mid-1800s through to 2017. We find that: 1) changes of government are associated with topic changes only when there is also a change in the party in power; 2) polling results appear dissociated from parliamentary topics; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change."
keywords: "text analysis, politics, Australia"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
bibliography: ../bibliography.bib
biblio-style: apsr
endnote: no
---

@@

# Introduction
New governments often go to some trouble to be different from the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was not supported by his immediate predecessor. Similarly, significant events can alter the course of a government. For instance, consider the change in the Howard government after the 9/11 attacks or the 2002 Bali bombings. However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party? And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?

@@

<!-- ```{r topicsoverdocuments, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over topics", fig.show = 'hold'} -->
<!-- document_1 <- tibble( -->
<!--   Topics = c( -->
<!--   "topic 1", "topic 2", "topic 3", "topic 4", "topic 5" -->
<!--   ), -->
<!--   Probability = c(0.40, 0.40, 0.1, 0.05, 0.05) -->
<!--   ) -->

<!-- document_2 <- tibble( -->
<!--   Topics = c( -->
<!--   "topic 1", "topic 2", "topic 3", "topic 4", "topic 5" -->
<!--   ), -->
<!--   Probability = c(0.01, 0.04, 0.35, 0.20, 0.4) -->
<!--   )   -->

<!-- par(mfrow=c(2,1)) -->
<!-- ggplot(document_1, aes(Topics, Probability)) + -->
<!--   geom_point() + -->
<!--   theme_classic() + -->
<!--   labs(title = "Distribution over topics for Document 1") + -->
<!--   coord_cartesian(ylim = c(0, 0.4)) -->

<!-- ggplot(document_2, aes(Topics, Probability)) + -->
<!--   geom_point() + -->
<!--   theme_classic() + -->
<!--   labs(title = "Distribution over topics for Document 2") + -->
<!--   coord_cartesian(ylim = c(0, 0.4)) -->
<!-- ``` -->

@@

<!-- ```{r topicsoverterms, cache = TRUE, echo=FALSE, out.width='.49\\linewidth', fig.cap = "Probability distributions over terms", fig.show = 'hold'} -->
<!-- topic_1 <- tibble( -->
<!--   Terms = c( -->
<!--   "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english" -->
<!--   ), -->
<!--   Probability = c(0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.0083, 0.2, 0.15, 0.4, 0.2) -->
<!--   ) -->

<!-- topic_2 <- tibble( -->
<!--   Terms = c( -->
<!--   "immigration", "race", "influx", "loans", "wealth", "saving", "chinese", "france", "british", "english" -->
<!--   ), -->
<!--   Probability = c(0.0142, 0.0142, 0.0142, 0.25, 0.35, 0.30, 0.0142, 0.0142, 0.0142, 0.0142) -->
<!--   )   -->

<!-- # par(mar = c(4, 4, 0.1, 0.1)) -->
<!-- ggplot(topic_1, aes(Terms, Probability)) + -->
<!--   geom_point() + -->
<!--   theme_classic() + -->
<!--   labs(title = "Distribution over terms for Topic 1") + -->
<!--   coord_cartesian(ylim = c(0, 0.4)) -->
<!-- ggplot(topic_2, aes(Terms, Probability)) + -->
<!--   geom_point() + -->
<!--   theme_classic() + -->
<!--   labs(title = "Distribution over terms for Topic 2") + -->
<!--   coord_cartesian(ylim = c(0, 0.4)) -->
<!-- ``` -->
